\chapter{Social Events}

\section{ACL 2025 Welcome Reception}
\vspace*{0.2cm}

Venue: Austria Center Vienna, Level 0 Hall E
Time: Sunday, July 27, 2025 18:30 - 20:30

Kick off ACL 2025 with an evening of networking, refreshments, and engaging conversations at our Welcome Reception! This gathering is the perfect opportunity to connect with fellow attendees, reconnect with colleagues, and immerse yourself in the vibrant natural language processing community before the conference begins in full.

Enjoy a relaxed atmosphere with light hors d’oeuvres and drinks as you meet researchers, practitioners, and industry leaders from around the world. Whether you're a first-time attendee or a returning participant, this reception sets the stage for an inspiring and productive conference experience.

Important Information:
Attendance is included for all Main Conference registrants.
If you are not registered for the Main Conference but would like to attend, you may add this event to your registration at the Registration Solution Desk located on the lobby level.

We look forward to welcoming you to ACL 2025!

Warm regards,
The ACL 2025 Organizing Committee

\section{ACL 2025 Social Event}
\vspace*{0.2cm}

Venue: Austria Center Vienna, Level 2 Hall A
Time: Tuesday, July 29, 2025 19:00 - 22:00

Join us for an unforgettable evening celebrating the spirit of Vienna, Austria. A perfect fusion of refinement, cultural exploration, and high-spirited fun, this event promises unforgettable moments for all in attendance.

\textbf{Entertainment Lineup}:
Enjoy the graceful artistry of Waltz Ballet
An exciting introduction to Voigasplattler, an energetic folk dance that showcases rhythmic precision and vibrant footwork
An electrifying performance by the Sugar Swing Cats

\textbf{Enjoy a delicious buffet dinner} featuring regional flavors
\textbf{Beer & wine tickets} available for guests

This is your chance to unwind, meet fellow attendees, and experience the best of Vienna’s artistic charm. We look forward to celebrating with you!

Important Information:
\textbf{Attendance is included} for all Main Conference registrants.
If you are not registered for the Main Conference but would like to attend, you may \textbf{add this event to your registration} at the Registration Solutions Desk.

Warm regards,
The ACL 2025 Organizing Committee
