\chapter{Anti-harassment Policy}
\vspace*{0.2cm}

ACL 2025 adheres to the ACL Anti-Harassment Policy. Any participant who experiences harassment or hostile behavior may contact any current member of the ACL Professional Conduct Committee or Jennifer Rachford, who is usually available at the registration desk of the conference. Please be assured that if you approach us, your concerns will be kept in strict confidence, and we will consult with you on any actions taken. The open exchange of ideas, the freedom of thought and expression, and respectful scientific debate are central to the aims and goals of a ACL conference. These require a community and an environment that recognizes the inherent worth of every person and group, that fosters dignity, understanding, and mutual respect, and that embraces diversity. For these reasons, ACL is dedicated to providing a harassment-free experience for participants at our events and in our programs. 
Harassment and hostile behavior are unwelcome at any ACL conference. This includes speech or behavior (including in public presentations and on-line discourse) that intimidates, creates discomfort, or interferes with a persons participation or opportunity for participation in the conference. We aim for ACL conferences to be an environment where harassment in any form does not happen, including but not limited to: harassment based on race, gender, religion, age, color, national origin, ancestry, disability, sexual orientation, or gender identity. 
Harassment includes degrading verbal comments, deliberate intimidation, stalking, harassing photography or recording, inappropriate physical contact, and unwelcome sexual attention. 
The ACL board members are listed at: https://www.aclweb.org/portal/about. 
The full policy and its implementation is defined at: https://aclweb.org/adminwiki/index.php?title=Anti\-Harassment\_Policy
