\chapter{Meal Info}
\vspace*{0.2cm}

\textbf{Breakfast}\\

\hspace{1cm} \textbf{July 27 - August 1}\\
\hspace{1cm} Breakfast is not provided, you can check with your local hotel and near by restaurants.\\

\textbf{Breaks $\dagger$}\\

\hspace{1cm} \textbf{July 27 - August 1}\\
\hspace{1cm} Coffee, tea, pastry, and fruit are provided late morning and midafternoon.\\

\textbf{Lunch}\\

\hspace{1cm} \textbf{July 27 - August 1}\\
\hspace{1cm} Lunch is not provided, however, the Austria Center Vienna will have lunch options available for purchase. See detailed agenda for times. \\

\textbf{Dinner}\\

\hspace{1cm} \textbf{July 27 - August 1}\\
\hspace{1cm} Dinner is  not provided, but there are plenty of cafes, and restaurants within the area.\\

\textbf{Social Events $\dagger$$\dagger$} \\

\textbf{Welcome Reception, July 27, 18:30 - 20:30}\\

Light canapes, and a drink ticket will be provided on Sunday, July 27, 2025, at the Welcome Reception. It will be held on Level 0 Hall E of the Austria Center Vienna.\\

\newpage
\textbf{Findings Reception, Monday, July 28, 2025 $\dagger$$\dagger$$\dagger$}\\
Light canapes, and refreshments will be provided on Monday, July 28, 2025, at the Findings Recpetion.  It will be held on Level 0 Hall E of the Austria Center Vienna.

\textbf{Social Event, July 29, 19:00 - 22:00}\\

Social Event Gala Dinner International Buffet Dinner and a drink ticket will be provided on Tuesday, July 29, 2025, at the Social Event Gala Dinner (Social Gala). Located in Level 2 Hall A of the Austria Center Vienna.

\vspace{4em}

$\dagger$: Included in Main Conference, Tutorial, and Workshop registrations.

$\dagger$$\dagger$: Included in the Main Conference registration only, and can be added on for Guests, Tutorials, Workshops, and Exhibitors to attend at the Registration Solutions Desk or through your YesEvents registration login. \textbf{No admission without an entry ticket}

$\dagger$$\dagger$$\dagger$: Included in the Main Conference registration only. No guest add ons for this reception
