\textbf{Message from the General Chair}

It is my great pleasure and honor to welcome you to the 63rd Annual Meeting of the Association for Computational Linguistics (ACL 2025), held in beautiful Vienna, Austria, from July 27 to August 1, 2025. ACL 2025 continues our field’s tradition of excellence in scholarship, innovation, and inclusivity, and I am deeply grateful to the many volunteers who have worked tirelessly to bring this event to life.

I want to express my deepest thanks to our Program Chairs ⏤ \textbf{Wanxiang Che, Joyce Nabende, Mohammad Taher Pilehvar} and \textbf{Ekaterina Shutova} ⏤ who have overseen the reviewing and selection process, and shaped a compelling and diverse scientific program. Overall, we received more than 8300 submissions and accepted 1700 at the main conference and 1392 as findings. This was made possible through close coordination with the ACL Rolling Review (ARR) team, led by the ARR Editors-in-Chief ⏤ \textbf{Jun Suzuki, Jing Jiang}, and \textbf{Xiaodan Zhu} ⏤ and I sincerely thank them. Although some improvements are still possible, the ARR workflow was already well integrated with the conference review and decision-making process. We are also deeply grateful to the (many!) Senior Area Chairs, Area Chairs, reviewers, and the Best Paper Committee (led by \textbf{Rada Mihalcea} and \textbf{Roi Reichart}), whose dedication ensured the high quality of our program. I am also grateful to our Technical Open Review Chairs, \textbf{Niket Tandon} and \textbf{Lizhen Qu}, for their behind-the-scenes work. For those joining virtually, our Virtual Infrastructure Chairs ⏤ \textbf{Manling Li, Yang Liu}, and \textbf{Avi Sil} ⏤ have worked to make the hybrid conference experience inclusive and engaging. I would also like to recognize the efforts of our Ethics Chairs ⏤ \textbf{Karën Fort} and \textbf{Bjorn Ross} ⏤ who have led the work aimed at ensuring that submissions meet the ethical standards of our field. 

ACL 2025 hosts a rich set of workshops and tutorials, thanks to the dedicated efforts of our Workshop Chairs ⏤ \textbf{Terra Blevins} and \textbf{Christophe Gravier} ⏤ and our Tutorial Chairs ⏤ \textbf{Yuki Arase, David Jurgens}, and \textbf{Fei Xia}. Our Demonstration Track Chairs ⏤ \textbf{Pushkar Mishra, Smaranda Muresan}, and \textbf{Tao Yu} ⏤ have put together an impressive set of system demonstrations of cutting-edge innovations in NLP. I am proud to say that we also have a rich Industry Track, thanks to \textbf{Yunyao Li} and \textbf{Georg Rehm} who created a “conference in the conference”. Given the growing interaction between academia and industry, I hope this tradition, which stems from NAACL and which I reinstated at ACL, will be continued in the following editions.
This conference could only have been made possible thanks to the invaluable work of our ACL Business Manager and Director of Events, \textbf{Jenn Rachford}, and her team — in particular, \textbf{Megan Haddad}, our ACL Administrator and Registration Manager — especially given the largest number of participants ever at ACL, estimated at the time of writing to be around 5000! Thanks also go to \textbf{Damira Mršic} and the Underline team for managing all content for the hybrid experience. The Local Organization Chairs, \textbf{Benjamin Roth} and \textbf{Dagmar Gromann}, worked hard on the bidding process, providing huge support with all local arrangements, the social event, and the visa process, eventually ensuring an outstanding experience for our in-person attendees. Our Visa Chairs ⏤ \textbf{Rexhina Blloshmi} and \textbf{Eleni Ilkou} ⏤ have helped numerous participants with their visa needs and any logistical difficulties in attending the conference. I also thank our Student Volunteer Chairs ⏤ \textbf{Pedro Henrique Luz de Araujo} and \textbf{Eleonora Mancini} ⏤ for their behind-the-scenes work, which will prove indispensable during the conference. 
Additional thanks go to \textbf{Zhu Liu, Mingyang Wang}, and \textbf{Jin Zhao}, our Student Research Workshop Chairs, who, with the support of faculty advisors \textbf{Lea Frermann, Daniel Hershcovich}, and \textbf{Tristan Miller}, devoted their work to supporting and mentoring the next generation of researchers. They also secured additional funding from the Vienna Meeting Fund ⏤ congratulations!
Our Publication Chairs ⏤ \textbf{Pierpaolo Basile, Libo Qin}, and \textbf{Zhenghao Liu} ⏤ have ensured timely and high-quality conference proceedings. I also thank the Handbook Chairs, \textbf{Els Lefever and Qiongkai Xu}, for assembling the handbook that will guide attendees through the conference program.
Of course our conference could not exist without the support of our sponsors! We are deeply grateful to our Sponsorship Chairs ⏤ \textbf{Raffaella Bernardi} and \textbf{Thomas Scialom} ⏤ and to \textbf{Chris Callison-Burch}, ACL’s Sponsorship Director, for securing the generous support that enables us to keep the conference accessible to as many participants as possible.
Fostering an inclusive environment remains a key goal of ACL. Our Diversity and Inclusion Chairs ⏤ \textbf{Senja Pollak, Maria Ryskina, Shane Storks}, and \textbf{Hwaran Lee} ⏤ have worked to support diverse participation and organize activities that reflect the global nature of our vibrant community. An inclusive ACL allows researchers from all areas and backgrounds to contribute, collaborate, and thrive ⏤ enriching both the scientific conversation and the broader societal impact of our work. We remain committed to building a community where everyone feels welcomed and valued.
Thank you to the Publicity and Social Media Chairs ⏤ \textbf{Anette Frank, Shruti Rijhwani}, and \textbf{Horacio Saggion} ⏤ for their communication work through social media, extending the conference’s reach to a wider audience. And this brings me to our Website and App Chairs ⏤ \textbf{Xudong Han} and \textbf{Alessandro Raganato} ⏤ who kept our community informed with timely updates about all aspects of the conference. The huge number of emails and communications that we received was smoothly managed throughout the year by our Internal Communication Chairs, \textbf{Sara Tonelli} and \textbf{Yiquan Wu}. We are very grateful!
I am particularly proud of the creation of a new role, the Documentation Chair, taken by \textbf{Chenghua Lin}, who did strenuous work to assemble a new handbook with up-to-date information coming from all chairs ⏤ whom I also thank for their valuable contributions ⏤ and maintain a clear and consistent record of all our processes. Given the speed at which all conference roles evolve in their duties and commitments, I hope this role will become standard in upcoming conferences to ensure a smooth transition.
Last but not least, I wish to thank the ACL Executive Committee for their guidance, and my fellow past General and Program Chairs, and especially \textbf{Claire Gardent} and \textbf{Colin Cherry}, for generously sharing their experience and insights.
ACL 2025 is a community-wide effort. Whether you are presenting a paper, leading a workshop or tutorial, volunteering, mentoring, supporting or attending to learn and connect, your presence and participation make a difference at this conference. Thank you for being part of it!
Welcome to Vienna. Welcome to ACL 2025!\\
\\
\textbf{Roberto Navigli}
Sapienza University of Rome & Babelscape
General Chair, ACL 2025
