\textbf{Message from the ACL Director of Events / Business Manager}\\
\\

On behalf of the ACL Executive team, I would like to extend my sincere gratitude to everyone who contributed to making ACL 2025 a reality.

A special thank you to our Local Committee—\textbf{Benjamin Roth} and \textbf{Dagmar Gromann}—as well as \textbf{Markus Heigl} from the Vienna Convention Bureau, our destination partner Meeting Destination Vienna, for their exceptional work throughout the submission and selection process. Your detailed planning and unwavering support helped bring ACL to this beautiful and historic city.

I also wish to thank the \textbf{ACL Boards} for their thoughtful review of venue bids and their decision to select Vienna, Austria as the host city. A particular note of appreciation goes to \textbf{David Yarowsky} for his guidance and efforts in finalizing our venue contracts.
To our organizational partners and extended team:

\begin{itemize}

\item \textbf{ACL Onsite Team}\\
 Megan Haddad – Event Assistant & ACL Admin


\item \textbf{Auxiliary Staff}\\
 Lina Staggs, Sally Stevenson, Brandy Dorsey, Karen Maloy, Jason Staggs


\item \textbf{Support Staff – Lee Hartman & Sons}\\
 Jon Dorsey – AV Director\\
 Trevor Laffoon – AV Tech


\item \textbf{Underline – Hybrid Event Partner}\\
 Damira Mrsic – Content & Hybrid Manager


\item \textbf{On-Site Support Team}\\
 Jernej Masnec, Borna Bevanda, Leticija Maričić, Petra Filipčić, Petra Vižintin, Rafael Grabovica, Lucijan Prpic, Nikola Pesut, Astrid Plišo, Kristijan Varga, Filip Cigic, Mihael Herenda, Petar Vođinac, Roko Mirković


\item \textbf{Austria Center Vienna}\\
 Friedrich Gehmacher – for your guidance and help in contracting the venue\\
 Victoria Wozniak – for managing the on-site logistics with care and precision


\item \textbf{Vendor Partners}\\
 Motto Catering\\
 Stand Out (Exhibition Services)\\
 XEST(Print Services)\\
 Marcelo Viridian (Graphics)\\

\item \textbf{Hotel Partners}
 Meliá Vienna\\
 NH Danube City\\
 Spark by Hilton Vienna Donaustadt\\


\item Finally, I want to express my heartfelt thanks to the entire \textbf{organizing and program committees}. Your dedication, long hours, and often sleepless nights have made ACL 2025 possible. Your commitment to academic excellence and community engagement is what makes this event a continued success year after year.

I look forward to a memorable and enriching conference here in Vienna, and I thank each of you for being a part of it.
With gratitude,


\textbf{Jennifer Rachford}\\
ACL Director of Events / Business Manager

